Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-03-14 ConferencePaper/DraftEdwardsWoods.Rnw
Added a table and a few graphics and made the files easier to work with in different file systems.

<<echo=FALSE, results=hide>>=
#This block reads in data and does some data cleaning and edits.
RECS <- read.csv("recs2009_public.csv")
library(plyr)
#ID
RECS$DOEID<-as.factor(RECS$DOEID)

@@

RECS$StrTenure<-relevel(RECS$StrTenure,"OwnSFDetached")

@

<<echo=FALSE,results=hide>>=
#work only with this subset
RECS<-RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]
@

@@

  \subsection{Race and Ethnicity Differences in Equipment and Structure}
  \subsection{Differences in Reported Behavior}

>>>>

<<DataEdit,echo=FALSE, results=hide>>=

#Saves time if the wrangling is already done.
if(file.exists("RECS.RData")) load("RECS.RData") else {
#This block reads in data and does some data cleaning and edits.
RECS <- read.csv("recs2009_public.csv")
library(plyr)
#ID
RECS$DOEID<-as.factor(RECS$DOEID)

@@

RECS$StrTenure<-relevel(RECS$StrTenure,"OwnSFDetached")
}

HUD <- read.csv("HUD.csv")

#And the clean up from importing from excell
HUD$pop<-as.numeric(gsub(",","",HUD$pop))
HUD$reportablen<-as.factor(HUD$reportablen)
@

<<DataSubsetMerge,echo=FALSE,results=hide>>=
#work only with this subset
RECS<-RECS[RECS$KOWNRENT!="Free" & RECS$NWEIGHT<40000 & RECS$NUMFRIG<5,]
if(!file.exists("RECS.RData"))save(RECS,file="RECS.RData")

#Merge the RECS and HUD together ***TODO***
@

@@

<<tabRaceVStruct,echo=false,results=tex>>=
library(xtable)
xtable(table(RECS$TYPEHUQ,RECS$Householder_Race), caption="Count of Observations by Race and Structure Type", label="tab:RaceVStruct")
@

\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
<<echo=false,fig=TRUE>>=
library(ggplot2)
qplot(KWH, data = RECS, xlim=c(0,30000),facets =Householder_Race~KOWNRENT, geom = "density" )
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Annual kWh by Income}
\label{fig:kWhbyIncome}
<<echo=false,fig=TRUE>>=
library(ggplot2)
qplot(Income,KWH, data = RECS, xlim=c(0,30000),facets =Householder_Race~KOWNRENT )+geom_boxplot()
@
\end{center}
\end{figure}

  \subsection{Race and Ethnicity Differences in Equipment and Structure}

  \subsection{Differences in Reported Behavior}

### 2015-03-14 ConferencePaper/DraftEdwardsWoods.tex
Added paper frame and empty biblography file as well as a notes section.
Page 16
Midpoint on the energy model.
Just a small change to demo pulls and pushes.
Added race and ethnicity when needed.  Added sections to show differences in equipment and behavior.
Moved the data wrangling to the paper draft and made copies of the data in a few places to make it easier to run with the push of a button.
Added a table and a few graphics and made the files easier to work with in different file systems.

\documentclass{article}
\author{Michael Edwards\\ 
  James Woods}
\title{Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption}

\begin{document}
\maketitle
\SweaveOpts{concordance=TRUE}

@@

  \subsection{Ethnicity in Conditional Demand}
  \subsection{How Ethnicity is Interpreted}

@@

>>>>

\documentclass{article}
\usepackage{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{1}

\author{Michael Edwards\\ 
  James Woods}
\title{Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption}

\usepackage{Sweave}
\begin{document}
\maketitle
\input{DraftEdwardsWoods-concordance}

@@

\cite{RBase}

  \subsection{Race and Ethnicity in Conditional Demand}
  \subsection{How Race and Ethnicity are Interpreted}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Sat Mar 14 21:27:10 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Wt & AfAm & NativeAm & Asian & Pacific & Other & Multi \\ 
  \hline
Mobile & 468 &  27 &   9 &   1 &   1 &   8 &   7 \\ 
  SFDetached & 6424 & 762 &  52 & 236 &  24 & 100 &  97 \\ 
  SFAttached & 649 & 131 &  12 &  48 &   2 &  20 &  16 \\ 
  SmApartment & 614 & 179 &  13 &  52 &   3 &  29 &  16 \\ 
  LgApartment & 1283 & 390 &  24 & 114 &  10 &  53 &  31 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-004}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Annual kWh by Income}
\label{fig:kWhbyIncome}
\includegraphics{DraftEdwardsWoods-005}
\end{center}
\end{figure}

  \subsection{Race and Ethnicity Differences in Equipment and Structure}

  \subsection{Differences in Reported Behavior}
